Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-25 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
added figures/ErosionBreak.pdf

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
 \newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
 \newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}

@@

@@

\subsection{Grow based on buffering}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G}$, where $d_\mathrm{G}$ is the growing 
distance, away 
from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

@@

Suppose that our start map is at scale $1:S_\mathrm{s}$, 
and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
The area of a building on map should be at least $a$ mm$^2$ so that the 
building is large enough to be perceived.
In \sect\ref{sec:Simplify}, we show that we set $a=4$.
Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
mm$^2$ at least, and
a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm (see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm so that 
it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, 
we define our growing distance as
\begin{equation}
\label{eq:d_G}
d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. 
A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.
During our growing, the growth at time $t$ is
\[
d_{\mathrm{G}, t} = t \cdot d_\mathrm{G}.
\]

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, we set the separation threshold 
$\epsilon= 0.2~\text{mm}$ on map. The separation threshold at time $t$ is
\[
d_{\epsilon, t} = t \cdot \epsilon (S_\mathrm{g}-S_\mathrm{s}).
\]

If two buildings become too close to each other during growing, 
we merge them by introducing a bridge connecting the nearest points 
(see \fig\ref{fig:GrowAndBridge}). 
Note that the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have the 
same widths.
We know where we should add bridges at time $t=0$. 
We grow the bridges together with the buildings.
We do not show the bridges until the two buildings are close enough 
which means that, in our case, 
the distance of two buildings is smaller than $d_{\epsilon,t}$.

%The distance between two buildings should be larger than a threshold, say, 
%$\epsilon$ mm on map.
%The real threshold distance is
%\begin{equation}
%\label{eq:d_epsilon}
%d_\epsilon= \epsilon  S_\mathrm{g}.
%\end{equation}
%
%If we insist on that we should observe 
%the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
%sure that
%\begin{equation}
%\label{eq:a_limit}
%\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
%\end{equation}
%Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
%and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
%\begin{equation}
%a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
%\end{equation}
%\textcite{Stoter2009} used $0.2$ mm as minimal distance between two buildings 
%on a map. We set our $\epsilon=0.2$.

\begin{figure}[tb]
	\centering
	\includegraphics{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
	too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.

@@

Show some results obtained by ArcGIS.

@@

\printbibliography
%\bibliographystyle{plainnat}
%%	\bibliography{References}
%\input{referenc}
\end{document}

>>>>

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
 \newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
 \newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}

@@

\newcommand{\dtrm}[1]{d_{\mathrm{#1},t}}

@@

\subsection{Grow based on buffering}
\label{sec:Grow}
We grow building based on buffering. 
There are two typical ways of buffering polygons, i.e.,
one with round joins and the other with miter joins (see 
\fig\ref{fig:Buffer_TwoKinds}).
As buildings are usually rectangles, 
we choose the second way because it is 
better at keeping the right angles.
If an angle is acute, however, an excessively long \emph{spike} will be 
produced.
This spike may go across other buildings 
(see \fig\ref{fig:Buffer_MiterLimits}~(a) for an example).
To avoid this kind of interruptions, 
we require that for an angle if a vertex of the 
buffer is more than $\alpha d_\mathrm{G}$, where $d_\mathrm{G}$ is the growing 
distance, away 
from the original vertex, 
a \emph{square} joining is applied
(see \fig\ref{fig:Buffer_MiterLimits}~(b)).
To keep right angles of buildings, 
we must have $\alpha \geq \sqrt{2}$. 
We set $\alpha  = 1.5$ so that a square joining is applied when an angle is 
smaller than $83.6 \degree$.

@@

Suppose that our start map is at scale $1:S_\mathrm{s}$, 
and our goal map is at scale $1:S_\mathrm{g}$ ($S_\mathrm{s}<S_\mathrm{g}$).
The area of a building on map should be at least $a$ mm$^2$ so that the 
building is large enough to be perceived.
In \sect\ref{sec:Simplify}, we show that we set $a=4$.
Accordingly, a square at the start map should have area $a S_\mathrm{s}^2$ 
mm$^2$ at least, and
a square at the goal map should have area $a S_\mathrm{g}^2$ mm$^2$ at least.
The difference of the side lengths is $\sqrt{a} (S_\mathrm{g}-S_\mathrm{s})$ 
mm (see \fig\ref{fig:Growth}).
A square on the start map needs to grow $\frac{1}{2}\sqrt{a} 
(S_\mathrm{g}-S_\mathrm{s})$ mm so that 
it can survive when users zoom out from 
the start map to the goal map.
In order to eliminate small buildings, 
we define our growing distance as
\begin{equation}
\label{eq:d_G}
d_\mathrm{G}=\frac{\lambda}{2}\sqrt{a} (S_\mathrm{g}-S_\mathrm{s}) \text{ 
	mm} \quad 0 < \lambda <1,
\end{equation}
where variable $\lambda$ is a growing factor. 
A larger $\lambda$ results in  
fewer buildings to be eliminated, and vice versa.
During our growing, the growth at time $t$ is
\begin{equation}
\label{eq:d_Gt}
\dtrm{G} = t \cdot d_\mathrm{G}.
\end{equation}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2~\text{mm}$ for target map. 
The separation threshold at time $t$ is
\[
d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s})).
\]

If two buildings become too close to each other during growing, 
we merge them by introducing a bridge connecting the nearest points 
(see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appear earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
For example, the two bridges in \fig\ref{fig:GrowAndBridge} at time $t=1$ have 
the same widths.
This setting is achieved by following.
We detect nearest points for each pair of buildings at time $t=0$ so that 
we know where we should add bridges. 
We grow the bridges together with the buildings,
but we do not show the bridges until the two buildings are close enough. 
\todo[inline]{actually larger than $d_{\epsilon, t}$.}

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
	too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes.
At time $t$, we dilate with distance $\dtrm{D}$, 
erode with distance $\dtrm{D}+\dtrm{E}$,
and dilate back with distance $\dtrm{E}$.

The buildings have been grown with distance $\dtrm{G}$ 
(see \sect\ref{sec:Grow}).
During the erosion, a part can be eroded with distance 
$\alpha (\dtrm{D}+\dtrm{E})$ at most.
In order not to break a building, the following condition must hold:
\[
\dtrm{G} + \dtrm{D} \ge \alpha (\dtrm{D}+\dtrm{E}),
\]
which means
\[
\dtrm{D} \le \frac{\dtrm{G}-\dtrm{E}}{\alpha - 1}.
\]

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{ErosionBreak}
	\caption{.}
	\label{fig:ErosionBreak}
\end{figure}
s

The separation threshold at time $t$ is
\[
d_{\epsilon, t} =t \cdot \epsilon S_\mathrm{g}.s
\]
One may expect that we define 
$d_{\epsilon, t} = \epsilon (S_\mathrm{s}+t(S_\mathrm{g}-S_\mathrm{s}))$
so that $\epsilon= 0.2~\text{mm}$ holds for a map at any scale.
The reason we do not define it as this way is that 
our growth $\dtrm{G}$ (see \eq\ref{eq:d_Gt}) can be arbitrarily small when $t$ 
is small.
In \sect\ref{sec:Simplify}, the erosion operator requires that

@@

Show some results obtained by ArcGIS.
Show the data at $1:50{,}000$.

@@

\printbibliography
\end{document}
